Meta RL analyses

### 2018-11-13 meta_RL_analyses.Rmd
Bugfixes

result_subdirs = c("basic", "nometa", "basic_su_heldout")

@@

@@

reward_d = reward_d %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = game_str %in% new_game_strs)
```

@@

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  gather(map_str, reward, -c(run, run_type, epoch)) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = source %in% new_game_strs | target %in% new_game_strs)
```

>>>>

result_subdirs = c("basic", "nometa", "basic_su_heldout", "nometa_su_heldout")

@@

new_game_strs_su_heldout = c("game_sum_under_l_1_bv_0_sr_0",
                             "game_sum_under_l_1_bv_1_sr_0",
                             "game_sum_under_l_1_bv_0_sr_1",
                             "game_sum_under_l_1_bv_1_sr_1")

@@

reward_d = reward_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (!is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout))
```

@@

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type)) %>%
  gather(map_str, reward, -c(run, run_type, is_su_ho, epoch)) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = (!is_su_ho & (source %in% new_game_strs | target %in% new_game_strs)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout)))
```
